The Title Goes Here with Each Initial Letter Capitalized

### 2018-04-23 2018/LeGo/LeGo.tex

\usepackage[numbers]{natbib}
\usepackage{rotating}
\usepackage{graphicx}
\pdfmapfile{+txfonts.map}

@@

\author{Victor Gergel}
\author{Konstantin Barkalov\corref{cor1}}
%\eaddress[url]{http://www.aip.org}
\author{Ilya Lebedev}
%\eaddress{anotherauthor@thisaddress.yyy}

\affil{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia.}
\corresp[cor1]{Corresponding author: konstantin.barkalov@itmm.unn.ru}

@@

\begin{abstract}
Abstract.
\end{abstract}

@@

@@

%One generator for random samples of two-dimensional test functions has been described in \cite{Grishagin1978,Grishagin2016}. This generator produces two-dimensional functions according to the formula
%\begin{eqnarray} \nonumber \label{VAG}
%\varphi(y)= -&\left\{\left(\sum^{7}_{i=1}\sum^{7}_{j=1}A_{ij}g_{ij}(y)+B_{ij}h_{ij}(y)\right)^2+\right. \\
%&\left.\left(\sum^{7}_{i=1}\sum^{7}_{j=1}C_{ij}g_{ij}(y)+D_{ij}h_{ij}(y)\right)^2\right\}^{1/2},\\ \nonumber
%\end{eqnarray}
%where $g_{ij}(y)=\sin(i\pi y_1)\sin(j\pi y_2)$, $h_{ij}(y)=\cos(i\pi y_1)\cos(j\pi y_2)$, $y=(y_1,y_2)\in R^2, \; 0 \leq y_1,y_2 \leq 1$, and coefficients $A_{ij}, B_{ij}, C_{ij}, D_{ij}$  are taken uniformly in the interval $[-1,1]$.

Let us consider a scheme for constructing the generator GCGen (Global Constrained optimization problem Generator) which allows to generate the test global optimization problems with $m$ constraints. Obviously, one can generate $m+1$ functions, the first $m$ of these ones can be considered as the constraints and the $(m+1)$-th function -- as the objective one. However, in this case, the conditional global minimizer of the objective function is unknown, and the preliminary estimate of this one (for example, by scanning over a uniform grid) will be time-consuming. At the same time, one could not control the size of the feasible domain. In particular, the constraints might be incompatible, and the feasible domain might be empty.

Below, the rules, which allow formulating the constrained global optimization problems so that:
\begin{itemize}
	\item one could control the size of feasible domain with respect to the whole domain of the parameters' variation;
	\item the global minimizer of the objective function would be known a priori taking into account the constraints;
	\item the global minimizer of the objective function without accounting for the constraints would be out of the feasible domain (with the purpose of simulating the behavior of the constraints and the objective function in the applied constrained optimization problems)
\end{itemize}
are proposed.

The rules defining the operation of the generator of the constrained global optimization with the properties listed above consist in the following.

\begin{enumerate}
	\item Let us generate $m+1$ functions $f_j(y), y \in D, 1 \leq j \leq m+1,$ by some generating scheme (for instance, by using the formula (\ref{VAG})). The constraints will be constructed on the base of the first $m$ functions, the $(m+1)$-th function will serve for the construction of the objective function.
	\item In order to know the global minimizer in the constrained problem a priori, let us make it to be the same to the global minimizer in the unconstrained problem. To do so, let us perform a linear transformation of coordinates so that the global minimizers of the constraint functions $y_j^\ast, \; 1 \leq j \leq m,$ would transit into the minimizer of the objective function $y_{m+1}^\ast$. This way, the functions $\overline{f_j}(y), \; 1 \leq j \leq m,$ with the same point of extremum will be constructed.
		\item In order to control the size of the feasible domain, let us construct an auxiliary function (a combined constraint)
		\[
		H(y)=\max_{1 \leq j \leq m}{\overline{f_j}(y)}
		\]
and compute its values in the nodes of a uniform grid in the domain $D$; the number of the grid nodes in the conducted experiments should be big enough (in our experiments it was $\min \left\{10^7, 10^{2N} \right\}$). Then, let us find the maximum and minimum values of the function $H(y)$ in the grid nodes, $H_{max}$ and $H_{min}$, respectively, and construct a characteristic $s(i)$ -- the number of points, in which the values of $H(y)$ fall into the range 
\[
\left[H_{min},H_{min}+i\frac{H_{max}-H_{min}}{100}\right], \; 1 \leq i \leq 100 .
\]
Then, the functions 
\[
\overline{f_j}(y) \leq q = H_{min}+i\frac{H_{max}-H_{min}}{100}, \; 1 \leq j \leq m,
\]
where $i$ is selected to be the minimal one satisfying the inequality
\[
\Delta \leq \frac{s(i)}{s(100)}
\]
will construct a problem with the feasible domain occupying the fraction $\Delta, \; 0<\Delta<1,$ of the whole search domain.
\item 
The test problem of global constrained optimization can be stated as follows
\[
\min\left\{ \varphi(y):y \in D, \; g_j(y)= \overline{f_j}(y)-q \leq 0, \; 1 \leq j \leq m \right\}
\]
where 
%$\varphi(y)=f_{m+1}(y)$. This problem will possess all declared properties (the fraction of the feasible domain will consist $\Delta$ of the whole search domain and the global minimizer of the constrained problem will be known).
%\item 
%In order to complicate the test constrained problem the form of the objective function can be expanded by the expression
\[
\varphi(y) = f_{m+1}(y)-\beta\sum_{j=1}^m\max\left\{0,\overline{f_j}(y) -q \right\}^\alpha,
\]
where $\alpha$ is a positive integer number and $\beta>0$ is selected in such a way as to provide the global minimum location of the function $\varphi(y)$ in the infeasible part of the search domain $D$. For instance, to guarantee this property the value of $\beta$ can be set as follows
\[
\beta>(h_{max}-h_{min})/(H_{max}-q)^\alpha,
\]
where $h_{max}$ and $h_{min}$ are the maximum and minimum values of the function $f_{m+1}(y)$ respectively.
\end{enumerate}

@@

В случае, если нужно сгенерировать задачу с заданным числом $S$ активных ограничений в точке условного минимума, то тогда правило 2 меняется следующим образом 
\begin{enumerate}
	\item В области поиска строится uniform grid с числом точек $\min \left\{10^7, 10^{2N} \right\}$, в каждой из которых вычисляются значения ограничений. 
	\item Определяется множество точек $\{y^t\}$, в которых активными являются $S$ ограничений; т.е. существуют такие номера $j_1, ...,j_S$, что $\left|g_{j_s}(y^t)\right|\leq \delta, \; 1\leq s \leq S$. В случае отсутствия такой точки, генерируется задача с произвольным числом активных ограничений и пользователь информируется об этом.
	\item Выбирается точка $y^* = \min_{t} \{\left\|\overline{y} - y^t\right\|\}$. Полученное грубое значение $y^*$ уточняется локальным методом. 
\end{enumerate}

@@

As an illustration, the level lines of the objective functions and the zero-level lines of the constraints for problems constructed on the base of functions (\ref{VAG}) with $\alpha = 3, \beta = 1$ and the volume fractions of the feasible domains $\Delta = 0.4, 0.6$ are shown in Fig.~\ref{fig:VAG}. The feasible domains are highlighted by green. The change of volume and, at the same time, the increase of complexity of the feasible domains are seen clearly. Fig.~\ref{fig:VAG} (a,b) also shows the points of 628 and 764 trials, correspondingly, performed by the \textit{index method} for solving constrained global optimization problems until the required accuracy $\epsilon=10^{-2}$ was achieved. The conditional optimizer is shown as a red point and the best estimation of the optimizer is shown as a blue point.

The index method has been proposed and developed in \cite{Strongin2000,Sergeyev2001,Barkalov2002}. The approach is based on a separate accounting for each constraint of the problem and is not related to the use of the penalty functions. According to the rules of index method, every iteration includes a sequential checking of fulfillment of the problem constraints at this point. The first occurrence of violation of any constraint terminates the trial and initiates the transition to the next iteration. This allows: (i) accounting for the information on each constraint separately and (ii) solving the problems, in which the function values may be undefined out of the feasible domain. It should be noted, that the index method can be efficiently parallelized for accelerators \cite{Barkalov2015,Barkalov2016}.

>>>>

\usepackage[numbers]{natbib}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{enumerate}
\pdfmapfile{+txfonts.map}

@@

\author{Victor Gergel\corref{cor1}}
\author{Konstantin Barkalov}
%\eaddress[url]{http://www.aip.org}
\author{Ilya Lebedev}
%\eaddress{anotherauthor@thisaddress.yyy}
\author{Maria Rachinskaya}

\affil{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia.}
\corresp[cor1]{Corresponding author: gergel@unn.ru}

@@

\begin{abstract}
В работе рассматривается дальнейшее развитие подхода к построению тестовых задач глобальной оптимизации с нелинейными ограничениями. Для порождаемых задач расположение глобального минимума является известным.
Отличительной чертой рассматриваемого генератора является возможность указания желаемого количества ограничений и доли допустимой области относительно все области глобального поиска. В обновленной версии генератора добавлена возможность формирования задач с условным минимумом, расположенным на границе допустимой области, и указания числа ограничений, активных в точке минимума. Демонстрация разработанного подхода приводится на примере известного индексного метода для решения сложных многоэкстремальных задач оптимизации с нелинейными ограничениями.
\end{abstract}

@@

В данной работе проводится дальнейшее развитие подхода для порождения задач глобальной оптимизации с нелинейными ограничениями, первоначально предложенного в \cite{Gergel2017}. При генерации тестовых задач может быть указано необходимое количество ограничений и желаемая доля допустимой области относительно все области глобального поиска. При этом для порождаемых задач расположение глобального минимума является известным, что существенно упрощает оценку результатов выполненных вычислительных экспериментов. В очередную версию генератора, в дополнение к указанным свойствам, были добавлены следующие возможности.
\begin{itemize}
	\item Возможность генерации задач с точкой условного минимума, расположенной на границе допустимой области.
	\item Возможность указания числа ограничений, активных в точке оптимума.
\end{itemize}
Указанные возможности позволяют на более высоком уровне имитировать свойства прикладных задач условной глобальной оптимизации.

@@

For example, one generator for random samples of two-dimensional test functions has been described in \cite{Grishagin2015}. This generator produces two-dimensional functions according to the formula
\begin{equation} \label{VAG}
\varphi(y)= -\left\{\left(\sum^{7}_{i=1}\sum^{7}_{j=1}A_{ij}g_{ij}(y)+B_{ij}h_{ij}(y)\right)^2 + \left(\sum^{7}_{i=1}\sum^{7}_{j=1}C_{ij}g_{ij}(y)+D_{ij}h_{ij}(y)\right)^2\right\}^{1/2},
\end{equation}
where $g_{ij}(y)=\sin(i\pi y_1)\sin(j\pi y_2)$, $h_{ij}(y)=\cos(i\pi y_1)\cos(j\pi y_2)$, $y=(y_1,y_2)\in R^2, \; 0 \leq y_1,y_2 \leq 1$, and coefficients $A_{ij}, B_{ij}, C_{ij}, D_{ij}$  are taken uniformly in the interval $[-1,1]$.

Another generator (\textit{GKLS generator}) for the functions of arbitrary dimensionality with known properties (the number of local minima, the size of their domains of attraction, the global minimizer, etc.) has been proposed in \cite{Gaviano2003}.  Application of this generator for studying some unconstrained optimization algorithms has been described in \cite{Paulavicius2014,Sergeyev2015}.

The generator GCGen (Global Constrained optimization problem Generator) which allows to generate the test global optimization problems with $m$ constraints на основе функций заданного класса, has been proposed in \cite{Gergel2017}. В данной статье были были предложены the rules, which allow formulating the constrained global optimization problems so that:
\begin{itemize}
	\item one could control the size of feasible domain with respect to the whole domain of the parameters' variation;
	\item the global minimizer of the objective function would be known a priori taking into account the constraints;
	\item the global minimizer of the objective function without accounting for the constraints would be out of the feasible domain.
\end{itemize}

@@

В случае, если нужно сгенерировать задачу с заданным числом $S$ активных ограничений в точке условного минимума, то тогда правила меняются следующим образом 
\begin{enumerate}
	\item Генерируется задача с произвольным расположением условного минимума $\overline{y}$;
	\item Из точки $\overline{y}$ с заданным шагом $h$ осуществляется покоординатный поиск допустимой точки $y^*$, для которой хотя бы одно из ограничений является активным, т.е. существует такой номер $j, 1 \leq j\leq m$, что $\left|g_j(y^*)\right| \leq \delta$.  
	\item Полученное грубое значение $y^*$ уточняется локальным методом. 
	\item Определяется число $K$ ограничений, активных в точке $y^*$.
	\item Если $K>S$, то из числа активных выбираются $K-S$ ограничений, и путем вычитания положительного параметра $q$ из правой части они переводятся в неактивные.
	\item Если $K<S$, то из числа неактивных выбираются $S-K$ ограничений, и путем прибавления положительного параметра $q$ в правой части они переводятся в активные.
	\item Выполняется преобразование координат, переводящее точку $\overline{y}$ в точку $y^*$. Тем самым целевая функция достигает своего минимума на границе feasible domain с заданным числом активных ограничений. 
\end{enumerate}

@@

As an illustration, the level lines of the objective functions and the zero-level lines of four constraints for the problem constructed on the base of functions (\ref{VAG}) with the volume fraction of the feasible domains $\Delta = 0.5$ are shown in Fig.~\ref{fig:VAG}. The feasible domains are highlighted by green.

Fig.~\ref{fig:VAG} (a,b,c,d) соответствуют разным способам генерации тестовых задач.
\begin{description}
	\item[(a)] Задача сгенерирована с расположением constrained optimizer внутри feasible domain.
	\item[(b)] Модификация задачи из п. (a): unconstrained optimizer находится вне feasible domain.
	\item[(c)] Модификация задачи из п. (b): constrained optimizer находится на границе feasible domain, число активных ограничений не задано.
	\item[(d)] Модификация задачи из п. (c): число активных ограничений задано равным двум.
\end{description}

Fig.~\ref{fig:VAG} (a,b,c,d) also shows the points of 628 and 764 trials, correspondingly, performed by the \textit{index method} for solving constrained global optimization problems until the required accuracy $\epsilon=10^{-2}$ was achieved. The conditional optimizer is shown as a red point and the best estimation of the optimizer is shown as a blue point.

The index method has been proposed and developed in \cite{Strongin2000,Sergeyev2001,Barkalov2002}. The approach is based on a separate accounting for each constraint of the problem and is not related to the use of the penalty functions. According to the rules of index method, every iteration includes a sequential checking of fulfillment of the problem constraints at this point. The first occurrence of violation of any constraint terminates the trial and initiates the transition to the next iteration. This allows: (i) accounting for the information on each constraint separately and (ii) solving the problems, in which the function values may be undefined out of the feasible domain. 
%It should be noted, that the index method can be efficiently parallelized for accelerators \cite{Barkalov2015,Barkalov2016}.
